Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
findings

We have been really impressed by the high quality of the QB and SKOS data. This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality. We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
\ke{in die conclusion sollte noch rein, dass constraint languages per se funktionieren zur erhöhung der datenqualität und deswegen mit hochdruck an der weiterentwicklung gearbeitet werden muss.}
% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

>>>>

We have been really impressed by the high quality of the QB and SKOS data. This is in contrast to the sometimes heard rumor that Linked Open Data lacks quality. We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
As the use of constraint languages per se enhances data quality, it must be continued working intensively on their further development.

%\ke{in die conclusion sollte noch rein, dass constraint languages per se funktionieren zur erhöhung der datenqualität und deswegen mit hochdruck an der weiterentwicklung gearbeitet werden muss.}
% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}
